\paperTitle

### 2014-05-07 doc/icml2014/assumption-proof.tex
Added figure to assumption proof
Updated piecewise likelihoods expression
Removed false statement about Z -> Y$

\begin{figure}
  \caption{A recursive construction of the conditional moments $\mOpp{v}{i}$.}
  \label{fig:message-proof}
\end{figure}

@@

\paragraph{Constructing $\mYpp{c}{\Pa(h_c)}$}

The algorithm constructs an expression for $\mYpp{t}{1}$ entirely as
  tensor multiplications of terms of the form $\mYpp{c}{\Pa(h_c)}$ for
  some hidden variable $h_c$. 
The individual $\mYpp{c}{\Pa(h_c)}$ can be easily computed from the
  clique marginals $Z_\sC$ as follows.

Without loss of generality, let $\sC \eqdef \{c\} \union \Pa(h_c)$ be a clique
  in the graph $\sG$.
If instead $\sC \subseteq \sC_1 \union \sC_2$ for some $\sC_1, \sC_2 \in
  \sG$, we can simply construct $Z_{\sC}$ from the union of $\sC_1$ and
  $\sC_2$,
\begin{align*}
  Z_\sC &= Z_{\sC_1} \times_{\del \sC} Z_{\sC_2},
\end{align*}
where $\del \sC = (\sC_1 \union \sC_2) \setminus \sC$.

Proceeding,
\begin{align*}
\mYpp{c}{\Pa(h_c)} 
  &\eqdef \Pr(h_c \given \Pa(h_c)) \\
  &= \frac{\Pr(h_c, \Pa(h_c))}{\Pr(\Pa(h_c))} \\
  &= Z_\sC \times_{\Pa(h_c)} \diag{Z_\sC(\ones, \cdot, \ldots, \cdot)}^{-1},
\end{align*}
where $\diag(\sP)$ is a ``diagonal'' tensor constructed by taking the
tensor product with $I^{\otimes p}$:
\begin{align*}
  \diag(\sP)[\vi,\vj] &\eqdef \sP[\vi] \delta[\vi,\vj].
\end{align*}

>>>>

\begin{figure}[t]
  \label{fig:message-proof}
  \centering
  \subimport{figures/}{assumption.tikz}
  \caption{A recursive construction of the conditional moments $\mOpp{v}{i}$. Shaded regions indicate participating variables in the intermediate distributions.}
\end{figure}

@@

% \paragraph{Constructing $\mYpp{c}{\Pa(h_c)}$}
% 
% The algorithm constructs an expression for $\mYpp{t}{1}$ entirely as
%   tensor multiplications of terms of the form $\mYpp{c}{\Pa(h_c)}$ for
%   some hidden variable $h_c$. 
% The individual $\mYpp{c}{\Pa(h_c)}$ can be easily computed from the
%   clique marginals $Z_\sC$ as follows.
% 
% Without loss of generality, let $\sC \eqdef \{c\} \union \Pa(h_c)$ be a clique
%   in the graph $\sG$.
% If instead $\sC \subseteq \sC_1 \union \sC_2$ for some $\sC_1, \sC_2 \in
%   \sG$, we can simply construct $Z_{\sC}$ from the union of $\sC_1$ and
%   $\sC_2$,
% \begin{align*}
%   Z_\sC &= Z_{\sC_1} \times_{\del \sC} Z_{\sC_2},
% \end{align*}
% where $\del \sC = (\sC_1 \union \sC_2) \setminus \sC$.
% 
% Proceeding,
% \begin{align*}
% \mYpp{c}{\Pa(h_c)} 
%   &\eqdef \Pr(h_c \given \Pa(h_c)) \\
%   &= \frac{\Pr(h_c, \Pa(h_c))}{\Pr(\Pa(h_c))} \\
%   &= Z_\sC \times_{\Pa(h_c)} \diag{Z_\sC(\ones, \cdot, \ldots, \cdot)}^{-1},
% \end{align*}
% where $\diag(\sP)$ is a ``diagonal'' tensor constructed by taking the
% tensor product with $I^{\otimes p}$:
% \begin{align*}
%   \diag(\sP)[\vi,\vj] &\eqdef \sP[\vi] \delta[\vi,\vj].
% \end{align*}
